# CreateSimulatePrepare {#CreateSimulatePrepare}


Here you can see the full process of creating a protocol with jsPsychMaker, simulating participants with jsPsychMonkeys and preparing the data with jsPsychHelpeR:


## Create protocol

Create a protocol with `jsPsychMaker::create_protocol()`:  

```{r, eval=FALSE}

# 1) Install jsPsychMaker
if (!require('remotes')) install.packages('remotes'); remotes::install_github("gorkang/jsPsychMaker")

# 2) Check available tasks
jsPsychMaker::list_available_tasks()$tasks

# 3) Create protocol
jsPsychMaker::create_protocol(canonical_tasks = c("AIM", "EAR", "IRI"),
                              folder_output = "~/Downloads/protocol999", 
                              launch_browser = FALSE)

```

You can now edit the configuration file (`~/Downloads/protocol999/config.js`) to adjust the project's parameters.  
  
  

## Simulate participants

Simulate participants with {jsPsychMonkeys}:  

```{r, eval=FALSE}

# 1) Install jsPsychMonkeys
if (!require('usethis')) install.packages('usethis'); usethis::use_course(url = "gorkang/jsPsychMonkeys", destdir = "~/Downloads/")

# 2) Setup
source("setup.R")

# 3) Change parameters
  # Go to _targets.R: Change parameter `local_folder_tasks` to your folder_output above. For example:  
  # - On Ubuntu, `local_folder_tasks = "~/Downloads/protocol999"`
  # - On Windows, `local_folder_tasks = "C:/Users/myusername/Downloads/protocol999"`

# 4) Run monkeys
targets::tar_make()

```

The monkeys responses csv's should be initially downloaded in your `Downloads` folder, and automatically moved to a `.data/` folder inside the protocol folder. For example, `~/Downloads/protocol999/.data`


## Prepare data 

Create a data preparation project with `jsPsychHelpeR::run_initial_setup()`:   

```{r, eval=FALSE}

# 1) Install
if (!require('remotes')) install.packages('remotes'); remotes::install_github("gorkang/jsPsychHelpeR")

# 2) Create project
jsPsychHelpeR::run_initial_setup(pid = "999", data_location = "~/Downloads/protocol999/.data", dont_ask = TRUE)

# 3) Restore all the necessary packages using {renv}
renv::restore(prompt = FALSE)

# 4) Run data preparation
targets::tar_make()

```

If you don't give a value to the `folder` parameter in `jsPsychHelpeR::run_initial_setup()`, the new project will be created in `~/Downloads/jsPsychHelpeRtest/`. After step 4), the prepared data can be found in the `outputs/data` folder of the new project, reports in  `outputs/reports`, etc.  
